Manuscript

### 2022-09-07 analysis/manuscript.Rmd
fix small typo

sig_confounders <- corr_potential_trait_confounders_pos_MVMR_summary %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding_MVMR) %>%
  mutate(total_potential_confounders = n()) %>%
  dplyr::summarize(description = outcome_description[1],
                   total_potential_confounders = total_potential_confounders[1],
                   potential_confounders = paste0(exposure_description, collapse = "; "), 
                   C_summ = corr_due_to_confounding_summ[1]) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  dplyr::rename(trait_description = description) %>% 
  dplyr::select(trait_description, trait_ID, everything())

@@

@@

```{r max_C_plot, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), message=FALSE, fig.height=10, dpi=600}

max_C_data <- corr_potential_trait_confounders_pos %>% filter(sig_confounder) %>% 
  #arrange(-corr_due_to_confounding_ratio) %>%
  mutate(total_potential_confounders = n()) %>%
  #slice_head(n = 1) %>%
  left_join(couple_MR_vs_trait_corr %>% 
              dplyr::rename(outcome_ID_IVW_beta = IVW_beta) %>%
              dplyr::rename(outcome_ID_IVW_se = IVW_se) %>%
              dplyr::rename(outcome_ID_couple_r = couple_r) %>% 
              dplyr::rename(outcome_ID_couple_r_se = couple_r_se) %>% 
              dplyr::select(outcome_ID, outcome_ID_IVW_beta, outcome_ID_IVW_se, outcome_ID_couple_r, outcome_ID_couple_r_se)) %>%
  mutate(same_trait_corr_minus_MR_est = abs(outcome_ID_couple_r)- abs(outcome_ID_IVW_beta)) %>%
  dplyr::rename(Z_beta = IVW_beta) %>%
  dplyr::rename(Z_se = IVW_se) %>%
  dplyr::rename(Z_pval = IVW_pval) %>%
  mutate(Z_sq_beta = Z_beta^2) %>%
  mutate(Z_sq_se = sqrt(4*Z_beta^2*Z_se^2+2*Z_se^4)) %>%
  dplyr::rename(Z_AM_beta = exposure_ID_AM_IVW_beta) %>%
  dplyr::rename(Z_AM_se = exposure_ID_AM_IVW_se) %>%
  mutate(Z_prod = Z_sq_beta*Z_AM_beta) %>%
  mutate(Z_prod_var = variance_of_product(Z_sq_beta, Z_sq_se, Z_AM_beta, Z_AM_se)) %>%
  mutate(Z_prod_se = sqrt(Z_prod_var)) %>%
  group_by(outcome_ID) %>% 
  mutate(corr_due_to_confounding_summ = sum(corr_due_to_confounding)) %>%
  mutate(corr_due_to_confounding_summ_SE = sqrt(sum(Z_prod_var))) %>%
  mutate(same_trait_corr_minus_MR_est_se = sqrt(variance_of_sum(outcome_ID_IVW_se, outcome_ID_couple_r_se))) %>%
  mutate(Phenotype = outcome_description) %>% 
  mutate(Phenotype = case_when(Phenotype == "Basal metabolic rate" ~ "BMR",
                               Phenotype == "Systolic blood pressure, automated reading" ~ "SBP",
                               Phenotype == "Pulse rate, automated reading" ~ "Pulse rate",
                               Phenotype == "Body fat percentage" ~ "BFP",
                               Phenotype == "Standing height" ~ "Height",
                               Phenotype == "Reticulocyte percentage" ~ "Reticulocyte %",

@@

max_C_plot <- ggplot2::ggplot(data = max_C_data, 
                              ggplot2::aes(x = corr_due_to_confounding_summ, 
                                           y = same_trait_corr_minus_MR_est, 
                                           label = Phenotype)) +

>>>>

sig_confounders <- corr_potential_trait_confounders_pos_MVMR_summary %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding_MVMR) %>%
  mutate(total_potential_confounders = n()) %>%
  dplyr::summarize(description = outcome_description[1],

                   total_potential_confounders = total_potential_confounders[1],
                   potential_confounders = paste0(exposure_description, collapse = "; "), 
                   max_C = max(corr_due_to_confounding_MVMR)) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  dplyr::rename(trait_description = description) %>% 
  dplyr::select(trait_description, trait_ID, everything())

@@

sig_confounders <- corr_potential_trait_confounders_pos_MVMR_summary %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding_MVMR) %>%
  mutate(total_potential_confounders = n()) %>%
  dplyr::summarize(description = outcome_description[1],

                   total_potential_confounders = total_potential_confounders[1],
                   potential_confounders = paste0(exposure_description, collapse = "; "), 
                   max_C = max(corr_due_to_confounding_MVMR)) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  dplyr::rename(trait_description = description) %>% 
  dplyr::select(trait_description, trait_ID, everything())

@@

```{r summ_C_plot, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), message=FALSE, fig.height=10, dpi=600}

summ_C_data <- corr_potential_trait_confounders_pos %>% filter(sig_confounder) %>% 
  #arrange(-corr_due_to_confounding_ratio) %>%
  mutate(total_potential_confounders = n()) %>%
  #slice_head(n = 1) %>%
  left_join(couple_MR_vs_trait_corr %>% 
              dplyr::rename(outcome_ID_IVW_beta = IVW_beta) %>%
              dplyr::rename(outcome_ID_IVW_se = IVW_se) %>%
              dplyr::rename(outcome_ID_couple_r = couple_r) %>% 
              dplyr::rename(outcome_ID_couple_r_se = couple_r_se) %>% 
              dplyr::select(outcome_ID, outcome_ID_IVW_beta, outcome_ID_IVW_se, outcome_ID_couple_r, outcome_ID_couple_r_se)) %>%
  mutate(same_trait_corr_minus_MR_est = abs(outcome_ID_couple_r)- abs(outcome_ID_IVW_beta)) %>%
  dplyr::rename(Z_beta = IVW_beta) %>%
  dplyr::rename(Z_se = IVW_se) %>%
  dplyr::rename(Z_pval = IVW_pval) %>%
  mutate(Z_sq_beta = Z_beta^2) %>%
  mutate(Z_sq_se = sqrt(4*Z_beta^2*Z_se^2+2*Z_se^4)) %>%
  dplyr::rename(Z_AM_beta = exposure_ID_AM_IVW_beta) %>%
  dplyr::rename(Z_AM_se = exposure_ID_AM_IVW_se) %>%
  mutate(Z_prod = Z_sq_beta*Z_AM_beta) %>%
  mutate(Z_prod_var = variance_of_product(Z_sq_beta, Z_sq_se, Z_AM_beta, Z_AM_se)) %>%
  mutate(Z_prod_se = sqrt(Z_prod_var)) %>%
  group_by(outcome_ID) %>% 
  mutate(corr_due_to_confounding_summ = sum(corr_due_to_confounding)) %>%
  mutate(corr_due_to_confounding_summ_SE = sqrt(sum(Z_prod_var))) %>%
  mutate(same_trait_corr_minus_MR_est_se = sqrt(variance_of_sum(outcome_ID_IVW_se, outcome_ID_couple_r_se))) %>%
  mutate(Phenotype = outcome_description) %>% 
  mutate(Phenotype = case_when(Phenotype == "Basal metabolic rate" ~ "BMR",
                               Phenotype == "Systolic blood pressure, automated reading" ~ "SBP",
                               Phenotype == "Pulse rate, automated reading" ~ "Pulse rate",
                               Phenotype == "Body fat percentage" ~ "BFP",
                               Phenotype == "Standing height" ~ "Height",
                               Phenotype == "Reticulocyte percentage" ~ "Reticulocyte %",

@@

max_C_plot <- ggplot2::ggplot(data = summ_C_data, 
                              ggplot2::aes(x = corr_due_to_confounding_summ, 
                                           y = same_trait_corr_minus_MR_est, 
                                           label = Phenotype)) +
